Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-09-06 doc/manuscript/manuscript.Rmd
finish edits to M&M

We used analysis of molecular variance (AMOVA) with Bruvo's genetic distance in *poppr* to test for differentiation associated with wmn by quantifying the differentiation conferred by Region, Source, and Year [@excoffier1992analysis; @bruvo2004simple; @kamvar2014poppr].
Source in this case was defined as a population belonging to a wmn or not.

To identify specific Regions that were more differentiated than others, we used discriminant analysis of principal components (DAPC) as implemented in *adegenet* version `r packageVersion("adegenet")`, assessing the per-sample posterior group assignment probability [@jombart2008adegenet]. 
This method decomposes the genetic data into principal components, and then uses a subset of these as the inputs for discriminant analysis, which attempts to minimize within-group variation and maximize among-group variation [@jombart2010discriminant]. 
To avoid over-fitting data, the optimal number of principal components was selected by using the *adegenet* function `xvalDapc()`. 
This function implements a cross-validation procedure to iterate over an increasing number of principal components on a subset (90%) of the data, trying to find the minimum number of principal components that maximizes the rate of successful group reassignment. 
To assess if cultivar had an influence on genetic diversity between wmn, we first subset the clone-corrected data to contain only samples from wmn and from the cultivars Beryl, Bunsi, and G122 and tested differentiation using AMOVA and DAPC as described above. 
We additionally assessed population stability over time by calculating DAPC over the combined groups of Region and Year as described above.

@@

We wanted to evaluate patterns of connectivity between shared multilocus haplotypes across geographic regions.
We first tabulated the multilocus haplotypes shared between at least two populations (defined as states or countries) with the *poppr* function `mlg.crosspop()` [@kamvar2014poppr].
From these data, we constructed a graph with populations as nodes and shared haplotypes as edges (connections) between nodes using the R packages *igraph* [@csardi2006igraph], *dplyr* version `r packageVersion("dplyr")` [@dplyr], and *purrr* version `r packageVersion("purrr")` [@purrr].
Each node was weighted by the fraction of shared MLHs.
Each edge represented a single MLH, but because a single MLH could be present in more than one population, that MLH would be represented by (*n*\*(*n*-1))/2 edges where n represents the number of populations crossed.
Edges were weighted by $1-P_{sex}$, where $P_{sex}$ is the probability of encountering the same haplotype via two independent meiotic events [@arnaud2007standardizing; @parks1993study].
We then used the `cluster_optimal()` function from *igraph* to define communities [@csardi2006igraph].
The graph was plotted using the R packages *ggplot2* version `r packageVersion("ggplot2")` [@ggplot2] and *ggraph* `r packageVersion("ggraph")` [@ggraph].
To ensure that we captured the same community signal, we additionally performed this analysis including the five polymorphic markers described above.

>>>>

We used analysis of molecular variance (AMOVA) with Bruvo's genetic distance in *poppr* to test for differentiation between populations in wmn and producer fields from the same region and collected in the same year [@excoffier1992analysis; @bruvo2004simple; @kamvar2014poppr].
To identify Regions with greater differentiation, we used discriminant analysis of principal components (DAPC) as implemented in *adegenet* version `r packageVersion("adegenet")`, assessing the per-sample posterior group assignment probability [@jombart2008adegenet]. 
This method decomposes the genetic data into principal components, and then uses a subset of these as the inputs for discriminant analysis, which attempts to minimize within-group variation and maximize among-group variation [@jombart2010discriminant]. 
To avoid over-fitting data, the optimal number of principal components was selected by using the *adegenet* function `xvalDapc()`. 
This function implements a cross-validation procedure to iterate over an increasing number of principal components on a subset (90%) of the data, trying to find the minimum number of principal components that maximizes the rate of successful group reassignment. 
To assess if cultivar had an influence on genetic diversity between wmn, we first subset the clone-corrected data to contain only samples from wmn and from the cultivars Beryl, Bunsi, and G122 and tested differentiation using AMOVA and DAPC as described above. 
We additionally assessed population stability over time by calculating DAPC over the combined groups of Region and Year as described above.

@@

We wanted to evaluate patterns of connectivity between shared multilocus haplotypes across geographic regions.
We first tabulated the multilocus haplotypes shared between at least two populations (defined as states or countries) with the *poppr* function `mlg.crosspop()` [@kamvar2014poppr].
From these data, we constructed a graph with populations as nodes and shared haplotypes as edges (connections) between nodes using the R packages *igraph* [@csardi2006igraph], *dplyr* version `r packageVersion("dplyr")` [@dplyr], and *purrr* version `r packageVersion("purrr")` [@purrr].
Each node was weighted by the fraction of shared MLHs.
Each edge represented a single MLH, but because a single MLH could be present in more than one population, that MLH would have a number of edges equivalent to the total number of possible connections, calculated as (*n*\*(*n*-1))/2 edges where n represents the number of populations crossed.
Edges were weighted by $1-P_{sex}$, where $P_{sex}$ is the probability of encountering the same haplotype via two independent meiotic events [@arnaud2007standardizing; @parks1993study].
This weighting scheme would thus strengthen the connection of edges that represented genotypes with a low probability of being produced via sexual reproduction. 
We then identified communities (among the Regions) in the graph using the `cluster_optimal()` function from *igraph* [@csardi2006igraph].
The graph was plotted using the R packages *ggplot2* version `r packageVersion("ggplot2")` [@ggplot2] and *ggraph* `r packageVersion("ggraph")` [@ggraph].
To ensure that we captured the same community signal, we additionally performed this analysis including the five polymorphic markers described above.
